Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions

### 2023-02-08 manuscript.Rmd
Update manuscript.Rmd

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge]. Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen. The substrates were mixed with a big roller and an excavator prepared the plots. The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B). The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively. The seeds were received from a commercial producer of autochthonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)). As expected have the hay meadows mixtures a higher specific leaf area (SLA) than the dry meadows mixtures<!--# describe difference --> . The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, *Bromus hordeaceus* was seeded as a nursery grass to provide safe sites under drought conditions.

@@

Write about traits.

@@

```{r tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for dry grassland 58. In total, seed mixtures had 16 or 32 g per plot. All individual seed mixtures are stored in the repository in Zenodo ('outputs/tables/table_a3_seedmixes')."}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all", j = -1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
  bold(part = "header", i = 1) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  autofit()
```

@@

```{r tab.id = "traits", tab.cap = "Traits"}
#read_csv(here::here("data", "raw", "data_raw_table_3.csv")) %>%
  #flextable() %>%
  #bold(part = "header") %>%
  #autofit()
```

## Table 3 {.unnumbered}

```{r tab.id = "substrate", ft.align = "left",tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction. Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005]. The pH was measured in CaCl2 solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract. For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33. To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C. Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand."}
read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
         show_col_types = FALSE) %>%
  select(-starts_with("lfl")) %>%
  slice(-1) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(
      here::here("data", "raw", "data_raw_table_3_substrate.csv"),
                 show_col_types = FALSE) %>%
      select(-starts_with("lfl")) %>%
      slice(1)
    ) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  align(align = "center", part = "all", j = -1) %>%
  compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
  compose(i = 1, j = 11, part = "header", value = as_paragraph("K", as_sub("2"), "O")) %>%
  compose(i = 1, j = 12, part = "header", value = as_paragraph("Mg", as_sup("2+"))) %>%
  compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  align(align = "left", part = "footer") %>%
  set_table_properties(layout = "autofit", width = 1)
```

@@

```{r figure-map, fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.  The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023]. Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D). The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates. The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_1_map.png")
  )
```

@@

@@

## Figure 3 {.unnumbered}

@@

@@

## Table S1 {.unnumbered}

```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Three dry years (2018–2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017–2021), based on weather station Metten [mean, 1981–2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping."}
read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
  autofit()
```

@@

## Table S2 {.unnumbered}

@@

>>>>

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge]. Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from removed agricultural soil of a dike construction site near Steinkirchen. The substrates were mixed with a big roller and an excavator prepared the plots. The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B). The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively. The seeds were received from a commercial producer of autochthonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:figure-traits)). As expected, the hay meadows mixtures have a higher specific leaf area (SLA) lower seed mass and higher canopy height than the dry meadows mixtures. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, *Bromus hordeaceus* was seeded as a nursery grass to provide safe sites under drought conditions.

@@

The functional traits specific leaf area (SLA), seed mass and canopy height were retrieved from the database LEDA [@Kleyer.2008] and TRY [@Kattge.2020].

@@

```{r tab.id = "seedmix", tab.cap = "Each plot received an individual set of 20 species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for dry grassland 58. In total, seed mixtures had 16 or 32 g per plot. All individual seed mixtures are stored in Table A3."}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all", j = -1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
  bold(part = "header", i = 1) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  autofit()
```

@@

```{r tab.id = "substrate", ft.align = "left", tab.cap = "Soil of the three substrates was analyzed for the fraction < 2mm fraction. Soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005]. The pH was measured in CaCl2 solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl2 extract. For calculating CaCO3, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33. To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C. Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand."}
read_csv(here::here("data", "raw", "data_raw_table_3_substrate.csv"),
         show_col_types = FALSE) %>%
  select(-starts_with("lfl")) %>%
  slice(-1) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(
      here::here("data", "raw", "data_raw_table_3_substrate.csv"),
                 show_col_types = FALSE) %>%
      select(-starts_with("lfl")) %>%
      slice(1)
    ) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  align(align = "center", part = "all", j = -1) %>%
  compose(i = 1, j = 10, part = "header", value = as_paragraph("P", as_sub("2"), "O", as_sub("5"))) %>%
  compose(i = 1, j = 11, part = "header", value = as_paragraph("K", as_sub("2"), "O")) %>%
  compose(i = 1, j = 12, part = "header", value = as_paragraph("Mg", as_sup("2+"))) %>%
  compose(i = 1, j = 14, part = "header", value = as_paragraph("CaCO", as_sub("3"))) %>%
  compose(i = 2, j = 10, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  compose(i = 2, j = 11, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  compose(i = 2, j = 12, part = "header", value = as_paragraph("mg 100g", as_sup("−1"))) %>%
  align(align = "left", part = "footer") %>%
  set_table_properties(layout = "autofit", width = 1)
```

@@

```{r fig.id = "figure-map", fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.  The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition [central photo; both aerial photos: @bayerischevermessungsverwaltung2023]. Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture types H and D). The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates. The photo on the bottom shows one block from the side after four years (Photo: Markus Bauer)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_1_map.png")
  )
```

@@

```{r fig.id = "figure-traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm_traits.tiff")
  )
```

## Figure 3

@@

@@

## Figure 7 {.unnumbered}

@@

## Table A1 <!--# Is it cited in the text? --> {.unnumbered}

```{r table-flood-weather, tab.id = "flood-weather", tab.cap = "Three dry years (2018–2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017–2021), based on weather station Metten [mean, 1981–2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping."}
read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
  autofit()
```

@@

## Table A2 <!--# Is it cited in the text? --> {.unnumbered}

@@

## Table A3 {.unnumbered}

Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->
